Scheeper's Meager-NWD Game and the Menger Game

### 2014-11-29 phd/dissertation/chapter5.tex
work on cantor tree space

\begin{defn}
  An $L$-space is a herditarally Lindel\"of, non-separable space.
\end{defn}

\begin{thm}
  Under $CH$(?), there exists a zero-dimensional, compact $L$-space.
  Furthermore, there exists a point-countable collection of clopen sets
  $\mc U=\{U_\alpha:\alpha<\omega_1\}$ in $X$ such
  that every point-finite subcollection of $\mc U$ is countable.
\end{thm}

\begin{proof}
  (TODO or find citation)
\end{proof}

\begin{defn}
  Let $\mb X=(X\times 2^{<\omega})\cup 2^\omega$ denote a Cantor tree
  of zero-dimensional, compact $L$-spaces $X$ with a point-countable collection
  of clopen sets $\mc U=\{U_\alpha:\alpha<\omega_1\}$ such
  that every point-finite subcollection of $\mc U$ is countable.
  The topology on $\mb X$ is
  given by decaring $U\times\{s\}$ to be an open
  neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
  open neighborhood $U$ of $x$ in $X$, and declaring
  $(U_\alpha\times\{f\rest n: m\leq n<\omega\})\cup\{f\}$ to be an open
  neighborhood of $f\in 2^\omega$ for each $\alpha<\omega_1$ and $m<\omega$.
\end{defn}

% \section{Cantor tree space example}

% \begin{ex}
%   Let $X$ be a zero-dimensional, compact L-space
%   (hereditarally Lindeloff and non-separable).
%   It is a fact that there exists a point-countable collection
%   $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is
%   also true that any point-finite subcollection of $\mathcal{U}$ is countable.

%   Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the
%   Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each
%   $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.

%   Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a
%   tree of $2^{<\omega}$ copies of $X$, and where
%   \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\]
%   is an open set about each $c_\alpha$.
% \end{ex}

>>>>

\begin{thm}
  There exists a compact, zero-dimensional topological space $X$
  such that $X$ has a point-countable cover
  $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of
  clopen sets which is not $\sigma$-point-finite.
\end{thm}

\begin{proof}
  (TODO)
\end{proof}

\begin{defn}
  Let $\mb X=(X\times 2^{<\omega})\cup C$ denote a Cantor tree
  of copies of a zero-dimensional, compact space $X$ with a point-countable
  cover $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of
  clopen sets which is not $\sigma$-point-finite, along with an uncountable
  subset of the Cantor set
  $C=\{c_\alpha:\alpha<\omega_1\}\in [2^\omega]^{\omega_1}$.
  The topology on $\mb X$ is
  given by decaring $U\times\{s\}$ to be a open
  neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
  open neighborhood $U$ of $x$ in $X$, and declaring
  $B_{\alpha,n}=(U_\alpha\times\{f\rest n: m\leq n<\omega\})\cup\{f\}$ to be
  an clopen neighborhood of $\alpha\in\omega_1$ for each $m<\omega$.
\end{defn}

\begin{lem}
  Let $F\in \omega_1^{<\omega}$ and $m<\omega$.
  Then $K_F$, $K_F'$, $L_m$ are compact in $\mb X$ as defined below.
  \[
    K_F = \bigcup_{\alpha \in F} B_{\alpha,0}
  \]
  \[
    A = \{z^\frown \<1\> : z \in \{0\}^{<\omega}\}
  \]
  \[
    K_F' = K_F \setminus (X \times A)
  \]
  \[
    L_m = X \times 2^{<m}
  \]
  Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
  for some $F\in C^{<\omega}$ and $m<\omega$.
\end{lem}

\begin{proof}
  $K_F$ contains $C_F=\{c_\alpha: \alpha\in F\}\subseteq C$, so any
  cover of basic open sets must include $B_{\alpha,n_\alpha}$ for each
  $\alpha\in F$, and the remaining uncovered portion of $K_F$ is a finite
  union of copies of closed subsets of compact $X$. Then $K_F'$ is also
  compact as it is a closed subset of $K_F$, and $L_m$ is compact as it
  is a finite union of copies of compact $X$.

  Let $D$ be compact. Consider the open cover
    \[
      \{
        B_{\alpha,0}
      :
        \alpha<\omega_1
      \}
      \cup
      \{
        X\times\{s\}
      :
        s\in 2^{<\omega}
      \}
    \]
  and note that the finite subcover for $D$ is a refinement of some
  $K_F'$ and $L_m$.
\end{proof}

\begin{thm}
  $\pl K\win\gruKPGame{\mb X}$.
\end{thm}

\begin{proof}
  Since $\{U_\alpha:\alpha<\omega_1\}$ is a point-countable cover,
  for each $x\in X$ let $\alpha_{x,n}<\omega_1$ yield
  ordinals such that $x\in U_{\alpha_{x,n}}$ for $n<\omega$.

  Let $M:\mb X\times \omega\to \mc K(\mb X)$ as follows:
    \[
      M(x,n)
        =
      \left\{
        \begin{array}{lcl}
          K_{\{\alpha_{x',m}:m\leq n\}}
        & : &
          x = \<x',s\> \in X\times 2^{<\omega}
        \\
          K_{\{\alpha\}}
        & : &
          x = c_\alpha \in C
        \end{array}
      \right.
    \]
  and use $M$ to define the strategy $\sigma$ for each $a\in\mb X^{<\omega}$:
    \[
      \sigma(a)
        =
      L_{|a|}
        \cup
      \bigcup_{i\leq |a|}
      M(a(i),|a|)
    \]

  Let $p:\omega\to\mb X$ be a legal attack against $\sigma$. Then as
  $p(n)\not\in L_n$, for each $x=\<x',s\>\in X\times 2^{<\omega}$,
  $X\times\{s\}$ is an open neighborhood of $x$ which contains finitely
  many $p(n)$.

  Then consider $x=c_\alpha$ for some $\alpha<\omega_1$. Then if
  $p(n)=\<x',s\>$ for some $n<\omega$, $x'\in U_\alpha$ or
  $p(n)=c_\alpha$, then
  $\alpha = \alpha_{p(n),N}$ for some $N<\omega$ and $p(m)\not\in B_{\alpha,0}$
  for $n+N<m<\omega$. Otherwise, $p(m)\not\in B_{\alpha,0}$ for any $m<\omega$.
  Either way, $B_{\alpha,0}$ is a neighborhood of $x$ which contains finitely
  many $p(n)$. Therefore, $\sigma$ is a winning strategy.
\end{proof}

We will show that there does not exist any winning $k$-Markov strategy for
$\pl K$ in this game. Knowledge of round number does not assist $\pl K$,
since she may force $\pl P$ to either stay within $C$, or to seed a growing
integer by forcing her to play outside $L_{|s|+1}$ in response to
$\<x,s\>\in X\times 2^{<\omega}$.

\begin{lem}
  If $\pl K\markwin\gruKPGame{\mathbb{X}}$, then
  $\pl K\tactwin\gruKPGame{\mathbb{X}}$.
\end{lem}

\begin{proof}
  TODO
  % Let $\sigma$ be a winning mark for $\pl K$ such that $m\leq n$ and
  % $r$ a subsequence of $s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
  % Define $n:\mb X\to\omega$ by
  %   \[
  %     n(x)
  %       =
  %     \left\{
  %       \begin{array}{lcl}
  %         |s|+1
  %       & : &
  %         x = \<x',s\> \in X\times 2^{<\omega}
  %       \\
  %         0
  %       & : &
  %         x \in C
  %       \end{array}
  %     \right.
  %   \]
  % and use $n$ to define the $k+1$-tactic $\tau$ by
  %   \[
  %     \tau(\emptyset)=\sigma(\emptyset,0)
  %   \]
  %   \[
  %     \tau(t\concat\<x\>)
  %       =
  %     L_{n(x)}
  %       \cup
  %     \{x\}
  %       \cup
  %     \sigma(t\concat\<x\>,n(x))
  %   \]

  % Let $p:\omega\to\mb X$ be a legal attack by $\pl P$ against $\tau$.
  % If $p(n)\in C$ for $n>N$, then since no $p(n)$ may be repeated,
  % $\{\{p(n)\}:N<n<\omega\}$ is a discrete collection, making
  % $\{\{p(n)\}:n<\omega\}$ locally finite.

  % Otherwise, let $q:\omega\to X\times 2^{<\omega}$ be the subsequence of $p$
  % removing points in $C$. If $q(0)=p(0)$, then
  %   \[
  %     q(0)
  %       =
  %     p(0)
  %       \not\in
  %     \tau(\emptyset)
  %       =
  %     \sigma(\emptyset,0)
  %   \]
  % and for any other $q(n)=p(m+1)=$
\end{proof}
